---
title: "Team6Project"
author: "Team 6"
date: "10/2/2020"
output: html_document
---
# Case Description
```{}
To predict whether the customer will open an account in our bank or not based on personal information and bank’s sale strategy. To obtain customer information from bank data, first perform a cluster analysis of these customer characteristics and establish a simulation model. When a certain characteristic classification is input into the model, it outputs the probability of his purchase, which provides a perspective for the bank's sales strategy to different customers. 
```
# Data Source
```{}
1. Title: Bank Marketing
2. Sources
   Created by: Paulo Cortez (Univ. Minho) and Sérgio Moro (ISCTE-IUL) @ 2012
3. Relevant Information:
   The data is related with direct marketing campaigns of a Portuguese banking institution. 
   The marketing campaigns were based on phone calls. Often, more than one contact to the same client was required, in order to access if the product (bank term deposit) would be (or not) subscribed. 
   
Citation:
  [Moro et al., 2011] S. Moro, R. Laureano and P. Cortez. Using Data Mining for Bank Direct Marketing: An Application of the CRISP-DM Methodology. 
  In P. Novais et al. (Eds.), Proceedings of the European Simulation and Modelling Conference - ESM'2011, pp. 117-121, Guimarães, Portugal, October, 2011. EUROSIS.

  Available at: [pdf] http://hdl.handle.net/1822/14838
                [bib] http://www3.dsi.uminho.pt/pcortez/bib/2011-esm-1.txt
```
```{r}
df <- read.csv("bank-full.csv",sep = ";")
head(df)
```
# Case Questions
```{}
What are the most important factors that may affect customers' decision to subscribe?
...
```
# Modelling Methodology
```{}

```
# Findings And Conclusion
```{}

```

# Source Code
### Required Libraries
```{r ,message = FALSE,warning=FALSE}
library(ggplot2)
library(MASS)
library(reshape2)
library(tidyverse)  # data manipulation
library(cluster)    # clustering algorithms
library(factoextra) # clustering algorithms & visualization
library(foreign)
```
### Data Loading
```{r}
bank <- read.csv("bank.csv",sep = ";")
# bank_full <- read.csv("bank-full.csv",sep = ";")
# head(bank)
# summary(bank)
```
### Data Cleaning
Make the table more readable and clear
```{r}
names(bank)[names(bank) == 'y'] <- 'ifPurchase'
bank$ifPurchase <- ifelse(bank$ifPurchase == "yes", T, F)
summary(bank$ifPurchase)
```

### Factor Analysis
Find the composition where it affects the result the most(eg. martial, job+martial)
Try to address what are the most important factors that may affect customers' purchase.
```{r}
fit1 <- lm(ifPurchase ~ ., data = bank)
summary(fit1)
```

### Clustering
```{r}
####### Tian Bingyang #######
library(tidyverse)  # data manipulation
library(cluster)    # clustering algorithms
library(factoextra) # clustering visualization
library(dendextend) # for comparing two dendrograms
bank_1 <- bank
bank_1$default <- ifelse(bank_1$default=='yes',1,0)
bank_1$housing <- ifelse(bank_1$housing=='yes',1,0)
bank_1$loan <- ifelse(bank_1$loan=='yes',1,0)
bank_1$outcome <- ifelse(bank_1$outcome=='yes',1,0)

#' Compute Gower distance
bank_2 <- bank[,1:8]
gower_dist <- daisy(bank_2, metric = "gower")
gower_mat <- as.matrix(gower_dist)
#' Print most similar clients
bank_2[which(gower_mat == min(gower_mat[gower_mat != min(gower_mat)]), arr.ind = TRUE)[1, ], ]

#' Print most dissimilar clients
bank_2[which(gower_mat == max(gower_mat[gower_mat != max(gower_mat)]), arr.ind = TRUE)[1, ], ]

## identify best options for clustering ##
sil_width <- c(NA)
for(i in 2:8){  
  pam_fit <- pam(gower_dist, diss = TRUE, k = i)  
  sil_width[i] <- pam_fit$silinfo$avg.width  
}
plot(1:8, sil_width,
     xlab = "Number of clusters",
     ylab = "Silhouette Width")
lines(1:8, sil_width)

## Summary of each cluster ##

k <- which.max(sil_width)
pam_fit <- pam(gower_dist, diss = TRUE, k)
pam_results <- bank_2 %>%
   mutate(cluster = pam_fit$clustering) %>%
   group_by(cluster) %>%
   do(the_summary = summary(.))
print(pam_results$the_summary)  ##print summary of each cluster


## Visualization in a lower dimensional space ##
tsne_obj <- Rtsne(gower_dist, is_distance = TRUE)
tsne_data <- tsne_obj$Y %>%
   data.frame() %>%
   setNames(c("X", "Y")) %>%
   mutate(cluster = factor(pam_fit$clustering))
ggplot(aes(x = X, y = Y), data = tsne_data) +
   geom_point(aes(color = cluster))

```

### Regression
```{r}

```

### Classification
Split data
```{r}
set.seed(123)
sample <- sample(c(TRUE,FALSE),nrow(bank),prob = c(0.75,0.25),replace = TRUE)  #generate random true and false
bank.train <- bank[sample, ] #those true data would be the training data
bank.test <- bank[!sample, ] # those data label as false would be the test data

####### Tian Bingyang - Naive Bayes ########
library(tidyverse)
library(ggplot2)
library(caret)
library(caretEnsemble)
library(psych)
library(Amelia)
library(mice)
library(GGally)
library(rpart)
library(randomForest)
library(e1071)
library(Rtsne)

## cluster  mannually (based on yifeng's cluster)##

bank$age_new <- ifelse(bank$age<=35,"19-35",ifelse(bank$age<=42,"36-42",ifelse(bank$age<=51,"43-51","52-87")))
bank$job_new <- bank$job
bank$job_new[bank$job!="services" & bank$job!="management" & bank$job!="blue-collar" & bank$job!="technician" & bank$job!="admin."]<- "unemployed"
bank$job_new[bank$job=="services" | bank$job=="management" | bank$job=="blue-collar" | bank$job=="technician" | bank$job=="admin."]<- "employed"
bank$balance_new <- ifelse(bank$balance<=700,"<=700",ifelse(bank$balance<=2819,"701-2819",ifelse(bank$balance<=8669,"2820-8669",">=8670")))

outliers <- filter(bank,campaign > 10)

bank <- bank[,c(-1,-2,-6)]
bank <- bank[,c(15:17,1:14)] ##reorder the columns
bank[,c(1:9,11,16,17)] <- lapply(bank[,c(1:9,11,16,17)], factor)  ## make variables factor


indxTrain <- createDataPartition(y = bank$outcome,p = 0.75,list = FALSE)
training <- bank[indxTrain,]
testing <- bank[-indxTrain,] 
prop.table(table(bank$outcome)) * 100


#create objects x which holds the predictor variables and y which holds the response variables
x = training[,c(1:16)]
y = training$outcome

model = train(x,y,'nb',trControl=trainControl(method='cv',number=10))

#Model Evaluation
#Predict testing set


model
Predict <- predict(model,newdata = testing )
values <- confusionMatrix(Predict, testing$outcome )
print(values)   ## output confusion matrix

#Plot Variable performance(importance)
X <- varImp(model)
plot(X)
```

